\chapter*{Disclaimer}


EazyCNC is program to control the operation of a CNC-Machine Tool.

TOAD4 is a microprocessos based controller board for controlling stepper motors.

EazyCNC and TOAD4 are intended for the hobbyist, they are not intended for 
for professional/commercial use.

Any machine tool is potentially dangerous. 

All electrical system have the potential to cause an electric shock or a fire hazard. 

All motorized systems can cause serious personal injury or damage to property.

All computer programs have design or implementation flaws (bugs) some of which can cause serious malfunction of the system.

Most countries and states have regulations and standards that govern the design, construction, use, deployment and placing on the market of electrical and mechanical equipment, including the software used to control them.

\emph{\color{red} No safety of design or construction or programming nor warranty is implied, instead it is the responsibility of whoever uses or deploys EazyCNC and/or TOAD4 to ensure that he/she understands the implications of using EazyCNC and/or TOAD4 and to comply with any legislation and codes of practice applicable to his/hers country or state. Further it is his/hers responsibility to ensure the safety of the system at all times}.

If you are in any doubt, you must seek guidance from a professionally qualified expert rather than risk injury or liability to yourself or to others.

SpareTimeLabs or Kustaa Nyholm cannot accept any responsibility resulting from the design, construction or use of EazyCNC and/or TOAD4.

All names of products and trademarks used in this manual are for example purposes only, no endorsement of any of them by SpareTimeLabs nor endorsement of EazyCNC or TOAD4 by their respective owners is implied.
